\Large\textbf{General Stage Untangling with Applications to Algorithm Derivation}

### 2014-06-02 paper/staging.tex
rename the pdfs

The theorem we want to show has two parts, one for the $\bbone$ code, and one for the $\bbtwo$ code.  
\begin{center}
\begin{tabular}{l}
If $\splitone [\emptyC]{e}{A}{c,l.r}$ \\
and $\rsone{e}{v}{q}$ \\
and $\reducetwo{q}{w}$ \\
then $\reduce{c}{\valprod{v}{u}}$ \\
and $\reduce{[u/l]r}{w}$
\end{tabular}
~~~
\begin{tabular}{l}
If $\splittwo[\emptyC]{e}{B}{p,l.r}$ \\
and $\rstwo{e}{q}$ \\
and $\reducetwo{q}{w}$ \\
then $\reduce{p}{u}$ \\
and $\reduce{[u/l]r}{w}$ 
\end{tabular}
\end{center}

@@

>>>>

The theorem we want to show has two parts, one for the $\bbone$ code, and one for the $\bbtwo$ code.  
\begin{center}
\begin{tabular}{l}
If $\splitone {e}{A}{c,l.r}$ \\
and $\colone {\gamma_1}{\Gamma}$ \\
and $\coltwo {\gamma_2}{\Gamma}$\\
and $\rsone{\gamma_1(e)}{v}{q}$ \\
and $\reducetwo{\gamma_2(q)}{w}$ \\
then $\reduce{|\gamma_1|(c)}{\valprod{v}{u}}$ \\
and $\reduce{[u/l]|\gamma_2|(r)}{w}$
\end{tabular}
~~~
\begin{tabular}{l}
If $\splittwo{e}{B}{p,l.r}$ \\
and $\colone {\gamma_1}{\Gamma}$ \\
and $\coltwo {\gamma_2}{\Gamma}$\\
and $\rstwo{\gamma_1(e)}{q}$ \\
and $\reducetwo{\gamma_2(q)}{w}$ \\
then $\reduce{|\gamma_1|(p)}{u}$ \\
and $\reduce{[u/l]|\gamma_2|(r)}{w}$ 
\end{tabular}
\end{center}

@@

% LET
\item {\bf Let (REALLY REALLY NOT DONE).} Suppose that
\begin{enumerate}
\item $\splitone{\next~e}{\fut A}{((),p),l.r}$
\item $\rsone{\next~e}{v}{q}$
\item $\reducetwo{q}{w}$
\end{enumerate}
By inversion of the splitting and reduction rules, we have
\begin{enumerate}
\item $\splittwo {e}{A}{p,l.r}$
\item $v$ has the form $()$
\item $\rstwo{e}{q}$
\end{enumerate}
We can now invoke the stage $\bbtwo$ part of the inductive hypothesis to yield,
\begin{enumerate}
\item $\reduce {p}{u}$
\item $\reduce {[u/l]r}{w}$
\end{enumerate}
It can then be directly proven that,
\begin{enumerate}
\item $\reduce {((),p)}{((),u)}$
\end{enumerate}
Which (along with the previous line) is what we wanted to show.
